\chapter{Introduction}\label{section:introduction}
\thispagestyle{pagestyle}


\section{CONTEXT}

Agriculture is a vital sector that plays a crucial role in sustaining human life and the economy.
Agriculture automation and optimization has become a major concern in recent years. 
As the global population continues to grow, the demand for food is increasing and the developing need for food
along with the effect of climate changes are forcing the agricultural industry to adapt and innovate\cite{OBAIDEEN2022100124}.

In the last 35 years, the wold has seen a doubling of the agricultural production. This has been achieved throught the use
of different fertilizers, pesticides and herbicides. This doubling was associated with a 6.87-fold increase in nitrogen fertilization,
a 3.48-fold increase in phosphorus fertilization and 1.68-fold increase in the amount of irrigated cropland \cite{doi:10.1073/pnas.96.11.5995}.
In addition, the water consumoption is expected to increase by 50\% by 2050 \cite{s20236865}. 

This project aims to address the challenges of water scarcity and the need of efficient irrigation systems
by presenting the plan, the implementation, the results and future work of a system that can be used in different
scenarios and is meant to help reducing the water consumption and increasing the agricultural productivity.
The PiIrrigate project intends achuive this by developing an innovative irrigation system that leverages the power of 
IoT and LoRa radio communication technologies.  
The main focus of this project is to create a system that can be easly used in different agricultural settings, 
starting from small gardens to large farms and even smart greenhouses. Beside this, I wanted to create a system that 
is easy to use and can be extended with ease. 

The ESP32 boards with sensors are responsible for colecting the data. Then data is sent using  LoRa to another
ESP32 board that acts as a gateway connected to a Raspberry Pi, which is responsible for sending the data to a web API.
The web API is developed in .NET and is responsible for storing the data in a PostgreSQL database.
The data is then sent to a web application using SignalR, which allows real-time communication between the server and the client.
The web application is responsible for displaying the live data and the historical data and also for providing a way to
control the system manually and to add new nodes to the system. 

This system takes advantage of the LoRa radio communication technology, 
which allows for long-range communication with low power consumption. Meaning that the system can be used in remote areas and
it will work even if the internet connection is not available to all the nodes. The Raspberry Pi is the only component of this system
that needs to be connected to the internet. Other components can be scatered on a area of 10km or more, depending on
the environment and the node setup (mesh or star topology).

\newpage
\section{MOTIVATION}


The reason why I choose to create such a system was fulled by my passion for technology and smart agriculture. Besides this,
I like to observe the data path, from the moment it is collected by the sensors, to the moment it is displayed
in a web application. 
I have always been intested in pieces of technology that can be used to solve real world problems and now I had the chance
to create such a system.

Initially, I wanted to create a system for my own lawn, but as I started working on the project, I realized that the system
can be used in many other scenarios, such as smart greenhouses or even large farms or vineyards. 

\chapter{State of the Art}\label{section:stateoftheart}

\section{Introduction}
The state of the art chapter provides an overview of the current state of smart irrigation 
systems and their applications in agriculture. 
This chapter will explore the existing technologies, methods, and solutions used in smart irrigation. 
It will also highlight the gaps and challenges in the current systems,
and how the PiIrrigate project aims to address these issues.

\section{Existing Smart Irrigation Solutions}
\subsection{Types of Smart Irrigation Systems}

There are several types of smart irrigation systems used in modern agriculture:

\begin{itemize}
  \item \textbf{Weather-Based Controllers} \\
  These systems use weather data to adjust irrigation schedules based on evapotranspiration rates, 
  ensuring that plants receive the right amount of water.

  \item \textbf{Soil Moisture-Based Controllers} \\
  These systems rely on data from soil moisture sensors placed in the root zone of the plants.
  Irrigation cycles are triggered when the soil moisture drops below a predetermined threshold, 
  ensuring plants receive water only when necessary.
  This method is very precise for specific zones\cite{smartIrrigationTechnologyControllersAndSensors}.

  \item \textbf{Hybrid Systems} \\
  Many modern systems utilize a hybrid approach, combining data from both
  weather feeds and soil moisture sensors for more accurate and resilient 
  irrigation decisions. Some research also explores "hybrid" in terms of 
  integrating different energy sources (e.g., solar and wind) to power the systems or 
  combining various 
  irrigation methods (like drip and sprinkler) under one smart control\cite{soilBasedIrrigation}.

  The PiIrrigate project place itself in the category of hybrid systems, using both
  soil moisture sensors and weather sensors to collect data.
  
  Some of the most popular hybrid smart irrigation systems include:
  \begin{itemize}
    \item \textbf{Netafim's Precision Irrigation System} \\
    This system cobines data from soil moisture and flow sensors with sattelite weather data and predictive
    analytics to optimize the irrigation proccess.
    
    Key features include:
    \begin{itemize}
      \item Real-time monitoring of soil moisture levels and weather forecasts.
      \item Automated irrigation scheduling based on weather forecasts.
      \item AI-based algorithms to optimize the irrigation timing and duration.
    \end{itemize}

    \item \textbf{CropX Smart Farming System} \\
    CropX is a cloud based platform that integrates soil moisture sensors, weather data and
    machine learning algorithms to optimize the irrigation process.

    Key features include:
    \begin{itemize}
      \item Irrigation recomandations based on soil variability, crop type and weather.
      \item Farmers can apply recommandations or integrate with automated irrigaitons contrllers.
      \item Easy to scale and adapt to different farm sizes from small to large-scale farms.
    \end{itemize}
  
    \item \textbf{Toro EVOLUTION® Series Controller with Smart ET Sensor} \\
    Combines basic sprinkler system hardware with smart sensors and connectivity,
    offering both manual and intelligent irrigation options. The evaporation sensors are used to measure
    the amount of water lost throught evaporation and adjust the irrigation accordingly.

    Key features include:
    \begin{itemize}
      \item Can be programmed manually or connected to a local weather station.
      \item Smart ET sensor measures evaporation rates and adjusts irrigation schedules.
      \item Compatible with smart devices for remote monitoring
    \end{itemize}
  \end{itemize}
\end{itemize}

\section{Comparative Analysis of Smart Irrigation Systems}
The table below provides a comparative analysis of some of the most popular smart 
irrigation systems available today and the PiIrrigate system.

\begin{table}[ht]
\centering
\begin{tabular}{|p{3.2cm}|p{3.2cm}|p{3.2cm}|p{3.2cm}|p{3.2cm}|}
\hline
\textbf{Feature} & \textbf{Netafim} & \textbf{CropX} & \textbf{Toro ET} & \textbf{PiIrrigate} \\
\hline
Irrigation Type & Drip & Any & Sprinkler & Custom \\
\hline
Automation & High (AI) & Med–High & Medium & Medium \\
\hline
Sensors & Soil, flow, weather & Soil, temp & ET sensor & Soil, temp, rain \\
\hline
Weather Data & Yes & Yes & Yes & Optional \\
\hline
Manual Control & App/cloud & App/web & Panel/app & Web UI \\
\hline
AI/Analytics & Yes & Yes & No & No \\
\hline
Scalability & Large farms & Small–large & Residential & Small farms/gardens \\
\hline
Cloud Sync & Yes & Yes & Optional & Yes \\
\hline
Use Case & Precision agri & Smart farming & Lawn care & Small to large scale\\
\hline
Cost & High & Med–High & Low–Mid & Low \\
\hline
\end{tabular}
\caption{Comparison of Smart Irrigation Systems}
\label{tab:irrigation_comparison}
\end{table}

\section{Identified Gaps and Challenges}
Despite the advancements in smart irrigation systems, several gaps and challenges remain:

\begin{itemize}
  \item \textbf{High Costs} \\
  Many existing systems are expensive, making them inaccessible for small farmers or home gardeners.
  
  \item \textbf{Complexity of Use} \\
  Some systems require specialized knowledge to set up and maintain, which can be a barrier for adoption.

  \item \textbf{Limited Customization} \\
  Many systems are designed for specific crops or environments, limiting their applicability in diverse agricultural settings.

  \item \textbf{Data Integration Issues} \\
  Integrating data from multiple sources (e.g., weather, soil sensors) can be challenging, leading to inefficiencies in irrigation management.
\end{itemize}

Bedside the presented gaps, there are also some other challenges that need to be addressed, such as:
data security and privacy concerns, the need for reliable internet connectivity in remote areas, 
and the need for systems that can operate in harsh environmental conditions. 

Another aspect that needs to be considered is the environmental impact of smart irrigation systems.
While these systems are designed to optimize water usage,
the production and disposal of electronic components can have a negative impact on the environment.
So another challenge is to create systems that are environmentally friendly and sustainable. This means 
that the components used in these systems shlould be madea from recyclable materials 
and the systems should be designed to have a long lifespan and to be easily repairable.

\section{Summary}
In summary, the state of the art in smart irrigation systems shows significant 
advancements in technology and methods, but also highlights several gaps and challenges 
that need to be addressed. The PiIrrigate project aims to fill these gaps by providing a
cost-effective, easy-to-use, and customizable solution that leverages the power of IoT and LoRa 
radio communication technologies.